Supplementary Content

### 2022-01-20 experiments/2_supplement/html_supplement.Rmd
correct sim duration effect figures in supplement

single_2e6 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/single_1e6_result.RDS"))
# sort(unique(ss_9s$CB_var_gmax_s))
# sort(unique(ss_9s$SB_var_gmax_s))
# ss_result <- ss_9s %>%
#   filter(abs(CB_var_gmax_s - 0.028254848) < 0.0001,
#          abs(SB_var_gmax_s - 0.084764545) < 0.0001,
#          abs(PB_var_gmax_s - 0.084764545) < 0.0001)

>>>>

single_2e6 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/single_2e6_result.RDS"))
# sort(unique(ss_9s$CB_var_gmax_s))
# sort(unique(ss_9s$SB_var_gmax_s))
# ss_result <- ss_9s %>%
#   filter(abs(CB_var_gmax_s - 0.028254848) < 0.0001,
#          abs(SB_var_gmax_s - 0.084764545) < 0.0001,
#          abs(PB_var_gmax_s - 0.084764545) < 0.0001)

temp <- single_2e6 %>%
  mutate(a = 10^a_O) %>%
  # arrange(a) %>%
  # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
  #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
  # select(-initial_N_CB, -a_O) %>%
  gather(species, quantity, 2:(ncol(.) - 2)) %>%
  mutate(
    var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
    functional_group = case_when(
      str_detect(species, "CB_") ~ "CB",
      str_detect(species, "SB_") ~ "SB",
      str_detect(species, "PB_") ~ "PB"
    ),
    log10_quantity = log10(quantity + 1)
  )
